---
output: github_document
---
# FM 871 Bonus Practical -HLVZ

This repository is dedicated to the bonus practical of the financial econometrics 871 course which investigates the varying impact of different fee levels on cumulative returns. Write up contained in `Tyranny_of_Fees.html` .

```{r, include = FALSE}
# load libraries
library(tidyverse);library(lubridate)

```


## Tyranny of Fees

We use the fmxdat::Jalshtr dataset which contains TRI data from 2002 to 2021. 

The first step is to transform the daily return to monthly, which is assigned to the `Jalshtr` variable in the `code/data_prep.R` script. 

```{r include=FALSE}
source("code/data_prep.R")
Jalshtr
```


Next, we create the function `Cum_Fee_Comparison` in the `code/Cum_Fee_Comp.R` script. This function creates a plot which illustrates the cumulative impact of fees on overall wealth. 

This is achieved by converting multiple levels of annually compounded fees as measured in basis points (10, 50, 100, 250, 350) into their monthly equivalent, this is deducted from gross returns for that month which is calculated in `Jalshtr` which yields the net returns for the month. Ratio of net to gross 


```{r echo=FALSE, warning=FALSE}
source("code/Cum_fee_comp.R")
Cum_Fee_Comparison(Jalshtr, Fee = 50*1e-4, Start = ymd(20020101), 
                               # Added purely for figure adjustment:
                               Gap = 3, Lvlset = 7,
                               mnthfwd = 18)
```

Let's compare the same but starting from 2010


```{r echo=FALSE, message=FALSE, warning=FALSE}
Cum_Fee_Comparison(Jalshtr, Fee = 50*1e-4, Start = ymd(20100101), 
                               # Added purely for figure adjustment:
                               Gap = 3, Lvlset = 3,
                               mnthfwd = 18)
```


