---
title: "Tyranny of Fees"
author: "Hendri van Zyl"
date: "`r Sys.Date()`"

bibliography: Tex/ref.bib
output:
  pagedown::html_paged:
    # template: wp_paged.html
    # css: ['wp.css', 'wp-fonts.css', 'wp-page.css']
    css: ["Template/default-fonts-Texevier.css", "Template/default-page-Texevier.css", "Template/default-Texevier.css"]
    csl: Template/harvard-stellenbosch-university.csl # referencing format used.
    template: ["Template/paged-Texevier.html"]

    toc: FALSE
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: TRUE

---

```{r setup, include = FALSE}

# Housekeeping
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
    #   Clear environment
rm(list = ls())
options(scipen = 999)

# load packages
library(pacman)
pacman::p_load(tidyverse, lubridate)

# load and transform the data 
source("code/data_prep.R")
Jalshtr

```

\newpage
## Introduction {-}

This document seeks to illustrate the effect of different management fee scales on cumulative returns of clients. 

We are using the Jalshtr total return index data that is accessible via the fmxdat package to measure the impact of various levels of fees on cumulative returns over time. 



## From inception {-}

First we compare the impact of the fee levels from the earliest available data point in 2002.

```{r echo=FALSE, message=FALSE, warning=FALSE}

source("code/Cum_Fee_Comp.R")
Cum_Fee_Comparison(Jalshtr, Fee = 50*1e-4, Start = ymd(20020101), 
                               # Added purely for figure adjustment:
                               Gap = 3, Lvlset = 7,
                               mnthfwd = 18)

```

## From 2010 {-}

Now let's compare that to starting with 2010 as the base year.  


```{r echo=FALSE}
Cum_Fee_Comparison(Jalshtr, Fee = 50*1e-4, Start = ymd(20100101), 
                               # Added purely for figure adjustment:
                               Gap = 3, Lvlset = 3,
                               mnthfwd = 18)
```


## Conclusion {-}

It is clear from these figures that compounding nature of fees have a dramatic impact on overall cumulative wealth over time. Investors should be keenly aware of this fact and take it into consideration when designing their their long term strategies. 
